---
title: "Glassdoor Reviews"
author: "katnoria"
url: "https://dash.sprinkleai.com/flexdash"
output: 
  flexdashboard::flex_dashboard:
    navbar: 
      - {title: "R Markdown", href: "https://dash.sprinkleai.com/reviews", alight: left}
---

```{r}
# Installation
# install.packages("flexdashboard")
# install.packages("leaflet")
```


```{r setup, include=FALSE}
library(flexdashboard)
library(leaflet)
library(dplyr)
library(ggplot2)
library(reshape2)
library(stringr)
library(treemap)

set.seed(12345)

reviews <- read.csv('data/employee_reviews.csv', stringsAsFactors = F)
reviews <- reviews %>%
  mutate(
    company = str_to_sentence(company),
    work.balance.stars = as.numeric(work.balance.stars), culture.values.stars=as.numeric(culture.values.stars),
    carrer.opportunities.stars=as.numeric(carrer.opportunities.stars),
    comp.benefit.stars=as.numeric(comp.benefit.stars), senior.mangemnet.stars=as.numeric(senior.mangemnet.stars)
    )

```

Overall {data-orientation=rows}
===================================== 

Row 
-----------------------------------------------------------------------

```{r}
overall_company_ratings <- reviews %>%
  group_by(company) %>%
  summarise(mean = round(mean(overall.ratings), 2))

plot_gauge <- function(company_name) {
  value <- overall_company_ratings %>%
    filter(company == company_name) %>%
    select(mean)
  g <- gauge(value$mean, min = 0.0, max = 5.0, symbol = '%', gaugeSectors(
    success = c(3.8, 5.0), warning = c(3.0, 3.8), danger = c(1.0, 3.0)
  ))
  return (g)
}  

# Get mean for all
mean_workbalance <- round(mean(reviews$work.balance.stars, na.rm = T), 2)
mean_culture <- round(mean(reviews$culture.values.stars, na.rm = T), 2)
mean_opportunities <- round(mean(reviews$carrer.opportunities.stars, na.rm = T), 2)
mean_benefits <- round(mean(reviews$comp.benefit.stars, na.rm = T), 2)
mean_seniormanagement <- round(mean(reviews$senior.mangemnet.stars, na.rm = T), 2)
```


### Amazon

```{r}
plot_gauge("Amazon")
```

### Apple

```{r}
plot_gauge("Apple")
```

### Facebook

```{r}
plot_gauge("Facebook")
```

### Google

```{r}
plot_gauge("Google")
```

### Microsoft

```{r}
plot_gauge("Microsoft")
```

### Netflix

```{r}
plot_gauge("Netflix")
```

Row
-----------------------------------------------------------------------

### Reviewer Location

```{r}
locations <- read.csv("data/locations_review_25above.csv")
reviews2 <- reviews %>%
  left_join(locations, by = "location") %>%
  select(c("location", "lat", "lon")) %>%
  filter(location != "none")

# Make sure locations is loaded (locations_review_25above.csv)
leaflet(reviews2) %>% addTiles() %>%
  addMarkers(clusterOptions = markerClusterOptions())
```


Row
-----------------------------------------------------------------------
### Ratings Heatmap

```{r}
ratings <- reviews %>%
  group_by(company) %>%
  summarise(
    work.balance = mean(work.balance.stars, na.rm = T), culture=mean(culture.values.stars, na.rm = T),
    opportunities=mean(carrer.opportunities.stars, na.rm = T), benefits=mean(comp.benefit.stars, na.rm = T),
    management=mean(senior.mangemnet.stars, na.rm = T))

melt(ratings) %>%
  ggplot(aes(x=variable, y=company, fill=value)) +
  geom_tile(color="white") +
  scale_fill_gradient2(low="red", high="darkgreen", mid="#ffffbf", midpoint = 3.0, limit=c(1.0, 5.0)) +
  xlab(NULL) +
  ylab(NULL)
```

### Overall Ratings

```{r}
reviews %>%
  select(c(company, overall.ratings)) %>%
  group_by(company, overall.ratings) %>%
  summarise(n=n()) %>%
  mutate(overall.ratings.pct = n/sum(n)) %>%
  ggplot(aes(overall.ratings, overall.ratings.pct, fill=company)) +
  labs(x="Rating", y="Reviews (%)", fill="Company") +
  geom_bar(stat = "identity") +
  facet_wrap(~company)
```


```{r}
filter_top20_titles <- function(company_name) {
  grouped_job_title <- reviews %>%
    filter(company == company_name) %>%
    group_by(job.title) %>%
    summarise(n=n()) %>%
      mutate(percent = n/sum(n)) %>%
      mutate(job.title = reorder(job.title, percent)) %>%
      top_n(20)
  
  return (grouped_job_title)
}

filter_top20_locations <- function(company_name) {
  grouped_job_title <- reviews %>%
    filter(company == company_name) %>%
    group_by(location) %>%
    summarise(n=n()) %>%
      mutate(percent = n/sum(n)) %>%
      mutate(job.title = reorder(location, percent)) %>%
      top_n(20)
  
  return (grouped_job_title)
}
```


Amazon {data-orientation=rows}
===================================== 

Row 
-----------------------------------------------------------------------

```{r}
indi_ratings <- function(company_name) {
  indi_ratings <- reviews %>%
    filter(company == company_name) %>%
    summarise(
      work.balance = round(mean(work.balance.stars, na.rm = T), digits = 2), 
      culture = round(mean(culture.values.stars, na.rm = T), digits = 2),
      opportunities = round(mean(carrer.opportunities.stars, na.rm = T), digits = 2), 
      benefits = round(mean(comp.benefit.stars, na.rm = T), digits = 2),
      management = round(mean(senior.mangemnet.stars, na.rm = T), digits = 2))  
  
    return (indi_ratings)
}

amzn_ratings <- indi_ratings("Amazon")
```

### Work/Life Balance

```{r}
# gauge(amzn_ratings$work.balance, min = 0.0, max = 5.0, symbol = '%', gaugeSectors(
#   success = c(3.7, 5.0), warning = c(3.0, 3.7), danger = c(1.0, 3.0)
# ))

show_valueBox <- function(value, benchmark) {
  return (
    valueBox(value, color = ifelse(value >= benchmark, "primary", "warning"))
  )
}
#valueBox(amzn_ratings$work.balance, color = ifelse(amzn_ratings$work.balance >= mean_workbalance, "success", "warning"))
show_valueBox(amzn_ratings$work.balance, mean_workbalance)
```

### Culture

```{r}
# gauge(amzn_ratings$culture, min = 0.0, max = 5.0, symbol = '%', gaugeSectors(
#   success = c(3.7, 5.0), warning = c(3.0, 3.7), danger = c(1.0, 3.0)
# ))
valueBox(amzn_ratings$culture, color = ifelse(amzn_ratings$culture >= mean_culture, "primary", "warning"))
```

### Opportunities

```{r}
# gauge(amzn_ratings$opportunities, min = 0.0, max = 5.0, symbol = '%', gaugeSectors(
#   success = c(3.7, 5.0), warning = c(3.0, 3.7), danger = c(1.0, 3.0)
# ))
valueBox(amzn_ratings$opportunities, color = ifelse(amzn_ratings$opportunities >= mean_opportunities, "primary", "warning"))
```

### Benefits

```{r}
# gauge(amzn_ratings$benefits, min = 0.0, max = 5.0, symbol = '%', gaugeSectors(
#   success = c(3.7, 5.0), warning = c(3.0, 3.7), danger = c(1.0, 3.0)
# ))
valueBox(amzn_ratings$benefits, color = ifelse(amzn_ratings$benefits >= mean_benefits, "primary", "warning"))
```

### Management Rating

```{r}
# gauge(amzn_ratings$management, min = 0.0, max = 5.0, symbol = '%', gaugeSectors(
#   success = c(3.7, 5.0), warning = c(3.0, 3.7), danger = c(1.0, 3.0)
# ))

valueBox(amzn_ratings$management, color = ifelse(amzn_ratings$management >= mean_seniormanagement, "primary", "warning"))
```

Row
-----------------------------------------------------------------------

### Job Titles with Most Reviews
```{r}
treemap(filter_top20_titles('Amazon'), 
                  index="job.title", 
                  vSize="percent", 
                  fontsize.labels=10,
                  palette=terrain.colors(10))
```

### Anonymous vs Rest Ratings Heatmap
```{r}
# treemap(filter_top20_locations('Amazon'), 
#                   index="location", 
#                   vSize="percent", 
#                   title=paste0("Top 20 Location"), 
#                   fontsize.labels=10,
#                   palette=terrain.colors(10))
anon_vs_rest_heatmap <- function(company_name) {
  heatmap <- reviews %>%
  mutate(reviewer_type = ifelse(
    str_detect(job.title, "Anonymous"),
    ifelse(str_detect(job.title, "Former Employee - Anonymous"), "Former Anonymous", "Current Anonymous"),
    "Rest of Employees"
  )) %>%
  filter(company == company_name) %>%
  group_by(reviewer_type) %>%
  summarise(
    work.balance = mean(work.balance.stars, na.rm = T), culture=mean(culture.values.stars, na.rm = T),
    opportunities=mean(carrer.opportunities.stars, na.rm = T), benefits=mean(comp.benefit.stars, na.rm = T),
    management=mean(senior.mangemnet.stars, na.rm = T)) %>% 
  melt() %>%
  ggplot(aes(x=variable, y=reviewer_type, fill=value)) +
  geom_tile(color="white") +
  scale_fill_gradient2(low="red", high="darkgreen", mid="#ffffbf", midpoint = 3.0, limit=c(1.0, 5.0)) +
  xlab(NULL) +
  ylab(NULL)
  
  return (heatmap)
}

anon_vs_rest_heatmap("Amazon")
```

Row
-----------------------------------------------------------------------

### Top 20 Words in Review Summary
```{r}

library("tm")
library("SnowballC")
library("wordcloud")
library("RColorBrewer")

# cleanup
# Function to clean the corpus
clean_text <- function(corpus, remove_extra_words) {
  corpus <- tm_map(corpus, content_transformer(tolower))
  corpus <- tm_map(corpus, removeWords, stopwords("english"))
  if (!missing(remove_extra_words)) {
    corpus <- tm_map(corpus, removeWords, remove_extra_words) 
  }
  corpus <- tm_map(corpus, removeNumbers)
  corpus <- tm_map(corpus, removePunctuation)
  corpus <- tm_map(corpus, stripWhitespace)
  return (corpus)
}

# convert to corpus
build_summary_df <- function(company_name) {
  data <- reviews %>%
    filter(company == company_name)
  
  corpus <- Corpus(VectorSource(data$summary))
  remove_misc <- c("-", "_")
  cleaned <- clean_text(corpus, remove_misc)
  tdm <- TermDocumentMatrix(cleaned)
  tdm <- as.matrix(tdm)
  tdm.sorted <- sort(rowSums(tdm), decreasing = TRUE)
  df <- data.frame(word = names(tdm.sorted), freq=tdm.sorted)
  return (df)
}
  
df_to_word_cloud <- function(df) {
  return (
    wordcloud(words = df$word,
                     freq=df$freq, min.freq=5,
                     max.words = 100, scale=c(3, .8),
                     colors=brewer.pal(8, 'Dark2'),
                    random.order=FALSE, rot.per=0.35,
                    use.r.layout=FALSE
                     )    
  )
}

amzn_summary_df <- build_summary_df("Amazon")

plot_20words_by_freq <- function(amzn_summary_df) {
    output <- amzn_summary_df %>%
      mutate(pct = freq/sum(freq), word=str_to_sentence(word)) %>%
      top_n(20, pct) %>%      
      mutate(word = reorder(word, pct)) %>%
      ggplot(aes(word, pct)) + 
      geom_bar(stat = "identity") + 
      xlab(NULL) + ylab(NULL) + 
      coord_flip()
  
    return (output)
}

plot_20words_by_freq(amzn_summary_df)
```

### Advice To Management
```{r}
# convert to corpus
build_mgmt_advice_df <- function(company_name) {
  data <- reviews %>%
    filter(company == company_name)
  
  corpus <- Corpus(VectorSource(data$advice.to.mgmt))
  remove_misc <- c("-", "_")
  cleaned <- clean_text(corpus, remove_misc)
  tdm <- TermDocumentMatrix(cleaned)
  tdm <- as.matrix(tdm)
  tdm.sorted <- sort(rowSums(tdm), decreasing = TRUE)
  df <- data.frame(word = names(tdm.sorted), freq=tdm.sorted)
  df <- df %>%
    filter(word != "none")
  return (df)
}

amzn_mgmt_df <- build_mgmt_advice_df("Amazon")
df_to_word_cloud(amzn_mgmt_df)
```


Apple {data-orientation=rows}
===================================== 

Row 
-----------------------------------------------------------------------

```{r}
aapl_ratings <- indi_ratings("Apple")
```

### Work/Life Balance

```{r}
# gauge(amzn_ratings$work.balance, min = 0.0, max = 5.0, symbol = '%', gaugeSectors(
#   success = c(3.7, 5.0), warning = c(3.0, 3.7), danger = c(1.0, 3.0)
# ))
show_valueBox(aapl_ratings$work.balance, mean_workbalance)
```

### Culture

```{r}
# gauge(amzn_ratings$culture, min = 0.0, max = 5.0, symbol = '%', gaugeSectors(
#   success = c(3.7, 5.0), warning = c(3.0, 3.7), danger = c(1.0, 3.0)
# ))
show_valueBox(aapl_ratings$culture, mean_culture)
```

### Opportunities

```{r}
# gauge(amzn_ratings$opportunities, min = 0.0, max = 5.0, symbol = '%', gaugeSectors(
#   success = c(3.7, 5.0), warning = c(3.0, 3.7), danger = c(1.0, 3.0)
# ))
show_valueBox(aapl_ratings$opportunities, mean_opportunities)
```

### Benefits

```{r}
# gauge(amzn_ratings$benefits, min = 0.0, max = 5.0, symbol = '%', gaugeSectors(
#   success = c(3.7, 5.0), warning = c(3.0, 3.7), danger = c(1.0, 3.0)
# ))
show_valueBox(aapl_ratings$benefits, mean_benefits)
```

### Management Rating

```{r}
# gauge(amzn_ratings$management, min = 0.0, max = 5.0, symbol = '%', gaugeSectors(
#   success = c(3.7, 5.0), warning = c(3.0, 3.7), danger = c(1.0, 3.0)
# ))
show_valueBox(aapl_ratings$management, mean_seniormanagement)
```

Row
-----------------------------------------------------------------------

### Job Titles with Most Reviews
```{r}
treemap(filter_top20_titles('Apple'), 
                  index="job.title", 
                  vSize="percent", 
                  fontsize.labels=8,
                  title = "",
                  palette=terrain.colors(10))
```

### Anonymous vs Rest Ratings Heatmap
```{r}
anon_vs_rest_heatmap("Apple")
```

Row
-----------------------------------------------------------------------

### Top 20 Words in Review Summary
```{r}

aapl_summary_df <- build_summary_df("Apple")

plot_20words_by_freq(aapl_summary_df)
```

### Advice to Management
```{r}
aapl_mgmt_df <- build_mgmt_advice_df("Apple")
df_to_word_cloud(aapl_mgmt_df)
```


Facebook {data-orientation=rows}
===================================== 

Row 
-----------------------------------------------------------------------

```{r}
fb_ratings <- indi_ratings("Facebook")
```

### Work/Life Balance

```{r}
# gauge(amzn_ratings$work.balance, min = 0.0, max = 5.0, symbol = '%', gaugeSectors(
#   success = c(3.7, 5.0), warning = c(3.0, 3.7), danger = c(1.0, 3.0)
# ))
show_valueBox(fb_ratings$work.balance, mean_workbalance)
```

### Culture

```{r}
# gauge(amzn_ratings$culture, min = 0.0, max = 5.0, symbol = '%', gaugeSectors(
#   success = c(3.7, 5.0), warning = c(3.0, 3.7), danger = c(1.0, 3.0)
# ))
show_valueBox(fb_ratings$culture, mean_culture)
```

### Opportunities

```{r}
# gauge(amzn_ratings$opportunities, min = 0.0, max = 5.0, symbol = '%', gaugeSectors(
#   success = c(3.7, 5.0), warning = c(3.0, 3.7), danger = c(1.0, 3.0)
# ))
show_valueBox(fb_ratings$opportunities, mean_opportunities)
```

### Benefits

```{r}
# gauge(amzn_ratings$benefits, min = 0.0, max = 5.0, symbol = '%', gaugeSectors(
#   success = c(3.7, 5.0), warning = c(3.0, 3.7), danger = c(1.0, 3.0)
# ))
show_valueBox(fb_ratings$benefits, mean_benefits)
```

### Management Rating

```{r}
# gauge(amzn_ratings$management, min = 0.0, max = 5.0, symbol = '%', gaugeSectors(
#   success = c(3.7, 5.0), warning = c(3.0, 3.7), danger = c(1.0, 3.0)
# ))
show_valueBox(fb_ratings$management, mean_seniormanagement)
```

Row
-----------------------------------------------------------------------

### Job Titles with Most Reviews
```{r}
treemap(filter_top20_titles('Facebook'), 
                  index="job.title", 
                  vSize="percent", 
                  fontsize.labels=8,
                  title = "",
                  palette=terrain.colors(10))
```

### Anonymous vs Rest Ratings Heatmap
```{r}
anon_vs_rest_heatmap("Facebook")
```

Row
-----------------------------------------------------------------------

### Top 20 Words in Review Summary
```{r}

fb_summary_df <- build_summary_df("Facebook")

plot_20words_by_freq(fb_summary_df)
```

### Advice To Management
```{r}
fb_mgmt_df <- build_mgmt_advice_df("Facebook")
df_to_word_cloud(fb_mgmt_df)
```


Google {data-orientation=rows}
===================================== 

Row 
-----------------------------------------------------------------------

```{r}
goog_ratings <- indi_ratings("Google")
```

### Work/Life Balance

```{r}
# gauge(amzn_ratings$work.balance, min = 0.0, max = 5.0, symbol = '%', gaugeSectors(
#   success = c(3.7, 5.0), warning = c(3.0, 3.7), danger = c(1.0, 3.0)
# ))
show_valueBox(goog_ratings$work.balance, mean_workbalance)
```

### Culture

```{r}
# gauge(amzn_ratings$culture, min = 0.0, max = 5.0, symbol = '%', gaugeSectors(
#   success = c(3.7, 5.0), warning = c(3.0, 3.7), danger = c(1.0, 3.0)
# ))
show_valueBox(goog_ratings$culture, mean_culture)
```

### Opportunities

```{r}
# gauge(amzn_ratings$opportunities, min = 0.0, max = 5.0, symbol = '%', gaugeSectors(
#   success = c(3.7, 5.0), warning = c(3.0, 3.7), danger = c(1.0, 3.0)
# ))
show_valueBox(goog_ratings$opportunities, mean_opportunities)
```

### Benefits

```{r}
# gauge(amzn_ratings$benefits, min = 0.0, max = 5.0, symbol = '%', gaugeSectors(
#   success = c(3.7, 5.0), warning = c(3.0, 3.7), danger = c(1.0, 3.0)
# ))
show_valueBox(goog_ratings$benefits, mean_benefits)
```

### Management Rating

```{r}
# gauge(amzn_ratings$management, min = 0.0, max = 5.0, symbol = '%', gaugeSectors(
#   success = c(3.7, 5.0), warning = c(3.0, 3.7), danger = c(1.0, 3.0)
# ))
show_valueBox(goog_ratings$management, mean_seniormanagement)
```

Row
-----------------------------------------------------------------------

### Job Titles with Most Reviews
```{r}
treemap(filter_top20_titles('Google'), 
                  index="job.title", 
                  vSize="percent", 
                  fontsize.labels=8,
                  title = "",
                  palette=terrain.colors(10))
```

### Anonymous vs Rest Ratings Heatmap
```{r}
anon_vs_rest_heatmap("Google")
```

Row
-----------------------------------------------------------------------

### Top 20 Words in Review Summary
```{r}

goog_summary_df <- build_summary_df("Google")

plot_20words_by_freq(goog_summary_df)
```

### Advice To Management
```{r}
goog_mgmt_df <- build_mgmt_advice_df("Google")
df_to_word_cloud(goog_mgmt_df)
```


Microsoft {data-orientation=rows}
===================================== 

Row 
-----------------------------------------------------------------------

```{r}
msft_ratings <- indi_ratings("Microsoft")
```

### Work/Life Balance

```{r}
# gauge(amzn_ratings$work.balance, min = 0.0, max = 5.0, symbol = '%', gaugeSectors(
#   success = c(3.7, 5.0), warning = c(3.0, 3.7), danger = c(1.0, 3.0)
# ))
show_valueBox(msft_ratings$work.balance, mean_workbalance)
```

### Culture

```{r}
# gauge(amzn_ratings$culture, min = 0.0, max = 5.0, symbol = '%', gaugeSectors(
#   success = c(3.7, 5.0), warning = c(3.0, 3.7), danger = c(1.0, 3.0)
# ))
show_valueBox(msft_ratings$culture, mean_culture)
```

### Opportunities

```{r}
# gauge(amzn_ratings$opportunities, min = 0.0, max = 5.0, symbol = '%', gaugeSectors(
#   success = c(3.7, 5.0), warning = c(3.0, 3.7), danger = c(1.0, 3.0)
# ))
show_valueBox(msft_ratings$opportunities, mean_opportunities)
```

### Benefits

```{r}
# gauge(amzn_ratings$benefits, min = 0.0, max = 5.0, symbol = '%', gaugeSectors(
#   success = c(3.7, 5.0), warning = c(3.0, 3.7), danger = c(1.0, 3.0)
# ))
show_valueBox(msft_ratings$benefits, mean_benefits)
```

### Management Rating

```{r}
# gauge(amzn_ratings$management, min = 0.0, max = 5.0, symbol = '%', gaugeSectors(
#   success = c(3.7, 5.0), warning = c(3.0, 3.7), danger = c(1.0, 3.0)
# ))
show_valueBox(msft_ratings$management, mean_seniormanagement)
```

Row
-----------------------------------------------------------------------

### Job Titles with Most Reviews
```{r}
treemap(filter_top20_titles('Microsoft'), 
                  index="job.title", 
                  vSize="percent", 
                  fontsize.labels=8,
                  title = "",
                  palette=terrain.colors(10))
```

### Anonymous vs Rest Ratings Heatmap
```{r}
anon_vs_rest_heatmap("Microsoft")
```

Row
-----------------------------------------------------------------------

### Top 20 Words in Review Summary
```{r}

msft_summary_df <- build_summary_df("Microsoft")

plot_20words_by_freq(msft_summary_df)
```

### Advice To Management
```{r}
msft_mgmt_df <- build_mgmt_advice_df("Microsoft")
df_to_word_cloud(msft_mgmt_df)
```


Netflix {data-orientation=rows}
===================================== 

Row 
-----------------------------------------------------------------------

```{r}
nflx_ratings <- indi_ratings("Netflix")
```

### Work/Life Balance

```{r}
# gauge(amzn_ratings$work.balance, min = 0.0, max = 5.0, symbol = '%', gaugeSectors(
#   success = c(3.7, 5.0), warning = c(3.0, 3.7), danger = c(1.0, 3.0)
# ))
show_valueBox(nflx_ratings$work.balance, mean_workbalance)
```

### Culture

```{r}
# gauge(amzn_ratings$culture, min = 0.0, max = 5.0, symbol = '%', gaugeSectors(
#   success = c(3.7, 5.0), warning = c(3.0, 3.7), danger = c(1.0, 3.0)
# ))
show_valueBox(nflx_ratings$culture, mean_culture)
```

### Opportunities

```{r}
# gauge(amzn_ratings$opportunities, min = 0.0, max = 5.0, symbol = '%', gaugeSectors(
#   success = c(3.7, 5.0), warning = c(3.0, 3.7), danger = c(1.0, 3.0)
# ))
show_valueBox(msft_ratings$opportunities, mean_opportunities)
```

### Benefits

```{r}
# gauge(amzn_ratings$benefits, min = 0.0, max = 5.0, symbol = '%', gaugeSectors(
#   success = c(3.7, 5.0), warning = c(3.0, 3.7), danger = c(1.0, 3.0)
# ))
show_valueBox(nflx_ratings$benefits, mean_benefits)
```

### Management Rating

```{r}
# gauge(amzn_ratings$management, min = 0.0, max = 5.0, symbol = '%', gaugeSectors(
#   success = c(3.7, 5.0), warning = c(3.0, 3.7), danger = c(1.0, 3.0)
# ))
show_valueBox(nflx_ratings$management, mean_seniormanagement)
```

Row
-----------------------------------------------------------------------

### Job Titles with Most Reviews
```{r}
treemap(filter_top20_titles('Netflix'), 
                  index="job.title", 
                  vSize="percent", 
                  fontsize.labels=8,
                  title = "",
                  palette=terrain.colors(10))
```

### Anonymous vs Rest Ratings Heatmap
```{r}
anon_vs_rest_heatmap("Netflix")
```

Row
-----------------------------------------------------------------------

### Top 20 Words in Review Summary
```{r}

nflx_summary_df <- build_summary_df("Netflix")

plot_20words_by_freq(nflx_summary_df)
```

### Advice To Management
```{r}
nflx_mgmt_df <- build_mgmt_advice_df("Netflix")
df_to_word_cloud(nflx_mgmt_df)
```

Common {data-orientation=column}
=====================================

This dashboard was developed using glassdoor reviews dataset available [here](https://www.kaggle.com/petersunga/google-amazon-facebook-employee-reviews).


The dataset contains over 67k employee reviews for Google, Amazon, Facebook, Apple, and Microsoft.
All the ratings are between 1-5.


| Field | Description |
| ----- | ----------- |
|Work/Life Balance Rating|1-5|
|Culture and Values Rating|1-5|
|Career Opportunities Rating|1-5|
|Comp & Benefits Rating|1-5|
|Senior Management Rating|1-5|

<!-- Common {data-orientation=column} -->
<!-- =====================================  -->
