---
title: "Employee Satisfaction Survey"
author: "katnoria"
output:
  html_document:
    df_print: paged
    toc: yes
  html_notebook:
    code_folding: hide
    theme: spacelab
    toc: yes
date: "16/03/2019"
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(knitr)
library(dplyr)
library(ggplot2)
library(stringr)
set.seed(12345)

reviews <- read.csv('data/employee_reviews.csv', stringsAsFactors = F)
head(reviews)
```


```{r}
# Convert ratings to double
reviews <- reviews %>%
  mutate(
    company = str_to_sentence(company),
    work.balance.stars = as.numeric(work.balance.stars), culture.values.stars=as.numeric(culture.values.stars),
    carrer.opportunities.stars=as.numeric(carrer.opportunities.stars),
    comp.benefit.stars=as.numeric(comp.benefit.stars), senior.mangemnet.stars=as.numeric(senior.mangemnet.stars)
    )

head(reviews, 1)
```

# Analysis

How many companies are there in the dataset?
```{r  echo=FALSE, warning=FALSE, message=FALSE}
reviews %>%
  group_by(company) %>%
  summarise(n=n()) %>%
  mutate(pct = n/sum(n)*100)
```

Show me the Ratings Info

```{r}
reviews %>%
  summarise(mean_overall_ratings=mean(overall.ratings), med_overall_ratings=median(overall.ratings))

reviews %>%
  group_by(overall.ratings) %>%
  summarise(n=n()) %>%
  ggplot(aes(overall.ratings, n)) + 
  geom_bar(stat = "Identity")
```


What are the top 10 reviewer location
```{r}
reviews %>%
  group_by(company, location) %>%
  summarise(n=n()) %>%
  filter(n > 10)
```

```{r}
library(leaflet)
locations <- read.csv("data/locations_review_25above.csv")
reviews2 <- reviews %>%
  left_join(locations, by = "location") %>%
  select(c("location", "lat", "lon")) %>%
  filter(location != "none")

# Make sure locations is loaded (locations_review_25above.csv)
# leaflet(reviews2) %>% addTiles() %>%
#   addMarkers(clusterOptions = markerClusterOptions())
```


## Overall Ratings

Rank the companies by overall ratings

```{r}
reviews %>%
  group_by(company) %>%
  summarise(ratings = mean(as.numeric(overall.ratings)), n=n())
```


```{r}
theme_Publication <- function(base_size=14, base_family="helvetica") {
      library(grid)
      library(ggthemes)
      (theme_foundation(base_size=base_size, base_family=base_family)
       + theme(plot.title = element_text(face = "bold",
                                         size = rel(1.2), hjust = 0.5),
               text = element_text(),
               panel.background = element_rect(colour = NA),
               plot.background = element_rect(colour = NA),
               panel.border = element_rect(colour = NA),
               axis.title = element_text(face = "bold",size = rel(1)),
               axis.title.y = element_text(angle=90,vjust =2),
               axis.title.x = element_text(vjust = -0.2),
               axis.text = element_text(), 
               axis.line = element_line(colour="black"),
               axis.ticks = element_line(),
               panel.grid.major = element_line(colour="#f0f0f0"),
               panel.grid.minor = element_blank(),
               legend.key = element_rect(colour = NA),
               legend.position = "bottom",
               legend.direction = "horizontal",
               legend.key.size= unit(0.2, "cm"),
               legend.margin = unit(0, "cm"),
               legend.title = element_text(face="italic"),
               plot.margin=unit(c(10,5,5,5),"mm"),
               strip.background=element_rect(colour="#f0f0f0",fill="#f0f0f0"),
               strip.text = element_text(face="bold")
          ))
      
}

```

```{r  echo=FALSE, warning=FALSE, message=FALSE}
ratings <- reviews %>%
  group_by(company) %>%
  summarise(ratings = mean(as.numeric(overall.ratings)), n=n())


ratings %>%
  mutate(company= reorder(company, ratings)) %>%
  ggplot(aes(company, ratings)) +
  labs(title="Employee Ratings", y="Rating", x="") + 
  geom_bar(stat="identity") +
  coord_flip()
```

Lets dig into the distribution of overall ratings
```{r echo=FALSE, warning=FALSE, message=FALSE}
# reviews %>%
#   select(c(company, overall.ratings)) %>%
#   ggplot(aes(overall.ratings, company)) + 
#   geom_point()
  
reviews %>%
  select(c(company, overall.ratings)) %>%
  ggplot(aes(overall.ratings, fill=company)) +
  xlab("Overall Rating") +
  ylab("Number of Reviews") + 
  geom_histogram(binwidth = 1) + 
  facet_wrap(~company)


  # ggplot(aes(y=company, x=overall.ratings)) +
  # geom_line(aes(group=company)) +
  # geom_point(aes(overall.ratings))

```

Amazon and Microsoft employees have left the most reviews. Lets see the review count for each company.

```{r  echo=FALSE, warning=FALSE, message=FALSE}

reviews %>%
  group_by(company) %>%
  summarise(n=n()) %>%
  mutate(company = reorder(company, n)) %>%
  ggplot(aes(company, n)) +
  labs(title="Number of survey participants", x="", y="Count of Participants") + 
  geom_bar(stat = "identity") + 
  coord_flip()
```

A better representation is to view the distribution of reviews by percent.
```{r  echo=FALSE, warning=FALSE, message=FALSE}
reviews %>%
  select(c(company, overall.ratings)) %>%
  group_by(company, overall.ratings) %>%
  summarise(n=n()) %>%
  mutate(overall.ratings.pct = n/sum(n)) %>%
  ggplot(aes(overall.ratings, overall.ratings.pct, fill=company)) +
  xlab("Overall Rating") +
  ylab("Reviews (%)") +
  geom_bar(stat = "identity") +
  facet_wrap(~company)

```

## Work/Life Balance

Rank the companies by work balance
```{r  echo=FALSE, warning=FALSE, message=FALSE}
reviews %>%
  group_by(company) %>%
  summarise(work.balance = mean(work.balance.stars, na.rm = T)) %>%
  mutate(company = reorder(company, work.balance)) %>%
  ggplot(aes(company, work.balance)) + 
  labs(title="Companies Ranked by Work/Life Balance", x="Work/Life Balance", y="Rating") +
  geom_bar(stat="identity") + 
  coord_flip()
```

We see that Google and Facebook lead the pack here.

## Ratings Heatmap

We can plot a heatmap of companies across multiple rating attributes.
```{r  echo=FALSE, warning=FALSE, message=FALSE}
library(reshape2)
library(ggplot2)

ratings <- reviews %>%
  group_by(company) %>%
  summarise(
    work.balance = mean(work.balance.stars, na.rm = T), culture=mean(culture.values.stars, na.rm = T),
    opportunities=mean(carrer.opportunities.stars, na.rm = T), benefits=mean(comp.benefit.stars, na.rm = T),
    management=mean(senior.mangemnet.stars, na.rm = T))

melt(ratings) %>%
  ggplot(aes(x=variable, y=company, fill=value)) +
  geom_tile(color="white") +
  labs(title="Employee Ratings Across All Categories") +
  scale_fill_gradient2(low="red", high="darkgreen", mid="#ffffbf", midpoint = 3.0, limit=c(1.0, 5.0)) +
  xlab(NULL) +
  ylab(NULL)

```


## Job Titles

Q: What is the distribution of job title ? 

```{r  echo=FALSE, warning=FALSE, message=FALSE}
reviews %>%
  group_by(company, job.title) %>%
  summarise(n=n()) %>%
  summarise(n=sum(n), unique_titles=length(unique(job.title)), pct=sum(n)/length(unique(job.title)))

```

## Top Reviewers

Who are top 10% of reviewers ?

```{r  echo=FALSE, warning=FALSE, message=FALSE}
top_ten_reviewers <- function(company_name)  {
  plot <- reviews %>%
    filter(company == company_name) %>%
    group_by(job.title) %>%
    summarise(n=n()) %>%
    mutate(freq = n/sum(n)) %>%
    mutate(job.title = reorder(job.title, freq)) %>%
    top_n(10) %>%
    ggplot(aes(job.title, freq)) + 
    geom_bar(stat="identity") + 
    labs(title = str_to_sentence(company_name), x="Job Title", y="Reviewers (%)") +
    coord_flip()
  
  return (plot)
}

# reviews %>%
#   filter(company == 'netflix') %>%
#   group_by(job.title) %>%
#   summarise(n=n()) %>%
#   mutate(freq = n/sum(n)) %>%
#   mutate(job.title = reorder(job.title, freq)) %>%
#   top_n(10) %>%
#   ggplot(aes(job.title, freq)) + 
#   geom_bar(stat="identity") + 
#   coord_flip()

top_ten_reviewers('Netflix')

```

Lets plot top 5 reviewers from  all five companies.
```{r echo=FALSE, warning=FALSE, message=FALSE, fig.height=7, fig.width=7, message=FALSE}
reviews %>%
  group_by(company, job.title) %>%
  summarise(n=n()) %>%
  mutate(freq = n/sum(n)) %>%
  mutate(job.title = reorder(job.title, freq)) %>%
  top_n(5) %>%
  ggplot(aes(job.title, freq)) + 
  geom_bar(stat="identity") + 
  coord_flip() + 
  facet_grid(~company)

```

You're correct. We cannot expect to find same job titles across the companies. But we now know a few things:

* Most reviewers are anonymous current or former employees
* There are very few facebook employees who post reviews as anonymous ?
* Google has the most anonymous current employee reviewers


Lets do it again, this time for each company separately.
```{r  echo=FALSE, warning=FALSE, message=FALSE}
top_ten_reviewers('Amazon')
top_ten_reviewers('Apple')
top_ten_reviewers('Facebook')
top_ten_reviewers('Google')
top_ten_reviewers('Microsoft')
```

Will treemap show the job titles better? Well, there is only one way to find out.

```{r  echo=FALSE, warning=FALSE, message=FALSE}
# install.packages("treemap")
library(treemap)

grouped_job_title <- reviews %>%
  filter(company == "Amazon") %>%
  group_by(job.title) %>%
  summarise(n=n()) %>%
  mutate(freq = n/sum(n)) %>%
  mutate(job.title = reorder(job.title, freq))

treemap(grouped_job_title, index="job.title", vSize="freq")

```

Nice, it can definitely go as #generativeart

However, its a bit difficult to read. If we restrict the plot to Top 20 job titles, we get 55% of the reviewers.

```{r  echo=FALSE, warning=FALSE, message=FALSE}
reviews %>%
  filter(company == "Amazon") %>%
  group_by(job.title) %>%
  summarise(n=n()) %>%
  mutate(freq = n/sum(n)) %>%
  mutate(job.title = reorder(job.title, freq)) %>%
  top_n(20) %>%
  tally(freq)
  
```


```{r  echo=FALSE, warning=FALSE, message=FALSE}

# plot_treemap <- function(company_name) {
#   grouped_job_title <- reviews %>%
#     filter(company == company_name) %>%
#     group_by(job.title) %>%
#     summarise(n=n()) %>%
#     mutate(percent = n/sum(n)) %>%
#     mutate(job.title = reorder(job.title, percent)) %>%
#     top_n(20)
#   
#   plot <- treemap(grouped_job_title, 
#                   index="job.title", 
#                   vSize="percent", 
#                   title=paste0("Top 20 Job Titles: ", company_name), 
#                   fontsize.labels=10,
#                   palette=terrain.colors(10))
#   return (plot)
#   
# }
# 
# The treemap function silently returns a list and we just need to show the plot
# z <- plot_treemap("Amazon")



filter_top20_titles <- function(company_name) {
  grouped_job_title <- reviews %>%
    filter(company == company_name) %>%
    group_by(job.title) %>%
    summarise(n=n()) %>%
      mutate(percent = n/sum(n)) %>%
      mutate(job.title = reorder(job.title, percent)) %>%
      top_n(20)
  
  return (grouped_job_title)
}

# Doing it this way works, just shows the plot
treemap(filter_top20_titles('Amazon'), 
                  index="job.title", 
                  vSize="percent", 
                  title=paste0("Top 20 Job Titles: Apple"), 
                  fontsize.labels=10,
                  palette=terrain.colors(10))

```
```{r}

treemap(filter_top20_titles('Apple'), 
                  index="job.title", 
                  vSize="percent", 
                  title=paste0("Top 20 Job Titles: Apple"), 
                  fontsize.labels=10,
                  palette=terrain.colors(10))

```
```{r}
company_name = "Facebook"
treemap(filter_top20_titles(company_name), 
                  index="job.title", 
                  vSize="percent", 
                  title=paste0("Top 20 Job Titles:", company_name), 
                  fontsize.labels=10,
                  palette=terrain.colors(10))

```

```{r}
company_name = "Google"
treemap(filter_top20_titles(company_name), 
                  index="job.title", 
                  vSize="percent", 
                  title=paste0("Top 20 Job Titles:", company_name), 
                  fontsize.labels=10,
                  palette=terrain.colors(10))

```

```{r}
company_name = "Microsoft"
treemap(filter_top20_titles(company_name), 
                  index="job.title", 
                  vSize="percent", 
                  title=paste0("Top 20 Job Titles:", company_name), 
                  fontsize.labels=10,
                  palette=terrain.colors(10))

```

```{r}
company_name = "Netflix"
treemap(filter_top20_titles(company_name), 
                  index="job.title", 
                  vSize="percent", 
                  title=paste0("Top 20 Job Titles:", company_name), 
                  fontsize.labels=10,
                  palette=terrain.colors(10))

```

## Anonymous Reviewers

Most reviewers are Anonymous, lets compare the distribution of overall rating between former and current anonymous reviewers

```{r  echo=FALSE, warning=FALSE, message=FALSE}
reviews %>%
  filter(str_detect(job.title, "Anonymous")) %>%
  group_by(company, overall.ratings, job.title) %>%
  summarise(n=n()) %>%
  mutate(overall.ratings.pct = n/sum(n), title=ifelse(str_detect(job.title, "Current"), "Current", "Former")) %>%
  ggplot(aes(overall.ratings, overall.ratings.pct, fill=title)) +
  geom_bar(position = "dodge", stat = "identity") + 
  labs(title="Overall Rating Distribution Between Current and Former Anonymous Reviewers", x="Overall Rating", y="Reviews (%)") +
  facet_wrap(~company)
```

```{r}
 reviews %>%
  mutate(reviewer_type = ifelse(
    str_detect(job.title, "Anonymous"),
    ifelse(str_detect(job.title, "Former Employee - Anonymous"), "Former Anonymous", "Current Anonymous"),
    "Rest"
  )) %>%
  filter(company == "amazon") %>%
  group_by(reviewer_type, overall.ratings) %>%
  summarise(n=n()) %>%
  mutate(overall.ratings.pct = n/sum(n)) %>%
  ggplot(aes(overall.ratings, overall.ratings.pct, fill=reviewer_type)) +
  geom_bar(position = "dodge", stat = "identity") + 
  labs(title="Overall Ratings Distribution: Anonymous and Other Reviewers", 
       x="Overall Rating", y="Reviews (%)",
       fill = "Reviewer Type")

```

Former reviewers tend to give lower ratings (between 1-3) compared to current. Perhaps, that is the reason they left in first place.
This is particularly noticable in Facebook and Netflix reviews.


```{r}
reviews %>%
  mutate(reviewer_type = ifelse(
    str_detect(job.title, "Anonymous"),
    ifelse(str_detect(job.title, "Former Employee - Anonymous"), "Former Anonymous", "Current Anonymous"),
    "Rest"
  )) %>%
  filter(company == "Amazon") %>%
  group_by(reviewer_type) %>%
  summarise(
    work.balance = mean(work.balance.stars, na.rm = T), culture=mean(culture.values.stars, na.rm = T),
    opportunities=mean(carrer.opportunities.stars, na.rm = T), benefits=mean(comp.benefit.stars, na.rm = T),
    management=mean(senior.mangemnet.stars, na.rm = T)) %>% 
  melt() %>%
  ggplot(aes(x=variable, y=reviewer_type, fill=value)) +
  geom_tile(color="white") +
  labs(title="Anonymous vs Rest Ratings in Each Category") +
  scale_fill_gradient2(low="red", high="darkgreen", mid="#ffffbf", midpoint = 3.0, limit=c(1.0, 5.0)) +
  xlab(NULL) +
  ylab(NULL)
```


Q: Can we identify the areas rated low ?

```{r echo=FALSE, warning=FALSE, message=FALSE}

reviews %>%
  filter(str_detect(job.title, "Former") & str_detect(job.title, "Anonymous"))%>%
  group_by(company) %>%
  summarise(
    work.balance = mean(work.balance.stars, na.rm = T), culture=mean(culture.values.stars, na.rm = T),
    opportunities=mean(carrer.opportunities.stars, na.rm = T), benefits=mean(comp.benefit.stars, na.rm = T),
    management=mean(senior.mangemnet.stars, na.rm = T)) %>% 
  melt() %>%
  ggplot(aes(x=variable, y=company, fill=value)) +
  geom_tile(color="white") +
  labs(title="Former Anonymous Employee Ratings in Each Category") +
  scale_fill_gradient2(low="red", high="darkgreen", mid="#ffffbf", midpoint = 3.0, limit=c(1.0, 5.0)) +
  xlab(NULL) +
  ylab(NULL)

```

The top reason was work/life balance, followed by management and opportunities.

```{r  echo=FALSE, warning=FALSE, message=FALSE}
reviews %>%
  filter(str_detect(job.title, "Current") & str_detect(job.title, "Anonymous"))%>%
  group_by(company) %>%
  summarise(
    work.balance = mean(work.balance.stars, na.rm = T), culture=mean(culture.values.stars, na.rm = T),
    opportunities=mean(carrer.opportunities.stars, na.rm = T), benefits=mean(comp.benefit.stars, na.rm = T),
    management=mean(senior.mangemnet.stars, na.rm = T)) %>% 
  melt() %>%
  ggplot(aes(x=variable, y=company, fill=value)) +
  geom_tile(color="white") +
  labs(title="Current Anonymous Employee Ratings in Each Category") +
  scale_fill_gradient2(low="red", high="darkgreen", mid="#ffffbf", midpoint = 3.0, limit=c(1.0, 5.0)) +
  xlab(NULL) +
  ylab(NULL)
```



# Text Analysis

In this section, We will perform text analysis on review summary, pros and cons as well as advice to management.

## Word Cloud 

We start by generating word cloud of review summary.

### Review Summary
Q: What are employees talking about in their reviews ?

We start by generating word cloud of summary data available in each review.

**Amazon**

```{r echo=FALSE, warning=FALSE, message=FALSE}
library("tm")
library("SnowballC")
library("wordcloud")
library("RColorBrewer")

# cleanup
# Function to clean the corpus
clean_text <- function(corpus, remove_extra_words) {
  corpus <- tm_map(corpus, content_transformer(tolower))
  corpus <- tm_map(corpus, removeWords, stopwords("english"))
  if (!missing(remove_extra_words)) {
    corpus <- tm_map(corpus, removeWords, remove_extra_words) 
  }
  corpus <- tm_map(corpus, removeNumbers)
  corpus <- tm_map(corpus, removePunctuation)
  corpus <- tm_map(corpus, stripWhitespace)
  return (corpus)
}

# convert to corpus
summary_cloud <- function(company_name) {
  data <- reviews %>%
    filter(company == company_name)
  
  corpus <- Corpus(VectorSource(data$summary))
  remove_misc <- c("-", "_")
  cleaned <- clean_text(corpus, remove_misc)
  tdm <- TermDocumentMatrix(cleaned)
  tdm <- as.matrix(tdm)
  tdm.sorted <- sort(rowSums(tdm), decreasing = TRUE)
  df <- data.frame(word = names(tdm.sorted), freq=tdm.sorted)
  wc <- wordcloud(words = df$word, freq=df$freq, min.freq=5, max.words = 100, scale=c(3, .8), colors=brewer.pal(8, 'Dark2'), main=company_name)
  
  output = list("company" = company_name, "data.frame" = df, "wordcloud" =  wc)
  return (output)
}

amzn_summary_plot <- summary_cloud("Amazon")
amzn_summary_plot$wordcloud
```

```{r}
plot_20words_by_freq <- function(summary_plot) {
    output <- summary_plot$data.frame %>%
      mutate(pct = freq/sum(freq)) %>%
      top_n(20, pct) %>%      
      mutate(word = reorder(word, pct)) %>%
      ggplot(aes(word, pct)) + 
      geom_bar(stat = "identity") + 
      labs(title = paste0("Top 20 words: ", summary_plot$company, x= NULL, y = NULL)) + 
      coord_flip()
  
    return (output)
}

plot_20words_by_freq(amzn_summary_plot)
```


**Apple**
```{r echo=FALSE, warning=FALSE, message=FALSE}

aapl_summary_plot <- summary_cloud("Apple")
aapl_summary_plot$wordcloud

```
```{r}
plot_20words_by_freq(aapl_summary_plot)  
```

**Facebook**
```{r echo=FALSE, warning=FALSE, message=FALSE}
fb_summary_plot <- summary_cloud('Facebook')
fb_summary_plot$wordcloud
```

```{r}
plot_20words_by_freq(fb_summary_plot)  
```


**Google**
```{r echo=FALSE, warning=FALSE, message=FALSE}
goog_summary_plot <- summary_cloud('Google')
goog_summary_plot$wordcloud
```

```{r}
plot_20words_by_freq(goog_summary_plot)  
```


**Microsoft**
```{r echo=FALSE, warning=FALSE, message=FALSE}
msft_summary_plot <- summary_cloud('Microsoft')
msft_summary_plot$wordcloud
```

```{r}
plot_20words_by_freq(msft_summary_plot)  
```


**Netflix**
```{r echo=FALSE, warning=FALSE, message=FALSE}
nflx_summary_plot <- summary_cloud('Netflix')
nflx_summary_plot$word_cloud
```

```{r}
plot_20words_by_freq(nflx_summary_plot)
```

If we combine the data frame of top 20 words from each company, will that show us any useful insight ?

```{r echo=FALSE, warning=FALSE, message=FALSE, fig.height=7, fig.width=7, message=FALSE}
library(tidyr)

filter_words <- c("Ever", "Get", "Call", "Can")

filter_20words_by_pct <- function(summary_plot) {
  company <- summary_plot$company
    output <- summary_plot$data.frame %>%
      filter(str_to_sentence(word) != company & !str_to_sentence(word) %in% filter_words) %>%
      mutate(pct = freq/sum(freq)) %>%
      top_n(20, pct) %>%
      select(c(word, pct)) 

    return (output)
}

amzn.top20words <- filter_20words_by_pct(amzn_summary_plot)
aapl.top20words <- filter_20words_by_pct(aapl_summary_plot)
fb.top20words <- filter_20words_by_pct(fb_summary_plot)
goog.top20words <- filter_20words_by_pct(goog_summary_plot)
msft.top20words <- filter_20words_by_pct(msft_summary_plot)
nflx.top20words <- filter_20words_by_pct(nflx_summary_plot)



all_top20words <- amzn.top20words %>%
  mutate(Amazon=pct) %>%
  select(-pct) %>%
  full_join(aapl.top20words, by = "word") %>%
  mutate(Apple=pct) %>%
  select(-pct) %>%
  full_join(fb.top20words, by = "word") %>%
  mutate(Facebook=pct) %>%
  select(-pct) %>%
  full_join(goog.top20words, by = "word") %>%
  mutate(Google=pct) %>%
  select(-pct) %>%
  full_join(msft.top20words, by = "word") %>%
  mutate(Microsoft=pct) %>%
  select(-pct) %>%
  full_join(nflx.top20words, by = "word") %>%
  mutate(Netflix=pct) %>%
  select(-pct)



all_top20words.ready <- all_top20words %>%
  mutate(word = str_to_sentence(word)) %>%
  gather(key="company", value="pct", -word)

all_top20words.ready %>%
  ggplot(mapping = aes(x=company, y=word, fill=pct)) +
  geom_tile() +
  scale_fill_gradient(name="Percent", low = "white", high = "darkgreen") + 
  labs(title="Most Common Words in Summary") +
  xlab(NULL) +
  ylab(NULL)
  

```


### Advice to Management

Q: What is their advice to senior management ?
```{r}
# convert to corpus
mgmt_advice_cloud <- function(company_name) {
  data <- reviews %>%
    filter(company == company_name & str_to_lower(advice.to.mgmt) != "none")
  
  corpus <- Corpus(VectorSource(data$advice.to.mgmt))
  remove_misc <- c("-", "_")
  cleaned <- clean_text(corpus, remove_misc)
  tdm <- TermDocumentMatrix(cleaned)
  tdm <- as.matrix(tdm)
  tdm.sorted <- sort(rowSums(tdm), decreasing = TRUE)
  df <- data.frame(word = names(tdm.sorted), freq=tdm.sorted)
  wc <- wordcloud(words = df$word, freq=df$freq, min.freq=5, max.words = 75, scale=c(3, .8), colors=brewer.pal(8, 'Dark2'), main=company_name)
  
  return (wc)
}

mgmt_advice_cloud("Amazon")
```


**Apple**
```{r}
mgmt_advice_cloud("Apple")
```

**Facebook**
```{r}
mgmt_advice_cloud("Facebook")
```

**Google**
```{r}
mgmt_advice_cloud("Google")
```

**Microsoft**
```{r}
mgmt_advice_cloud("Microsoft")
```

**Netflix**
```{r}
mgmt_advice_cloud("Netflix")
```
